\vspace{-1cm}\Large{\textsf{The Size Distribution of Firms and Industrial Water Pollution: A Quantitative Analysis of China} \\ \textsf{Replication Instructions}}

### 2019-09-19 Documentation/Replication_Instruction.tex
ready for submission

% Set header and footer
\usepackage{fancyhdr}
\pagestyle{fancy}
\fancyhead{}
\fancyhead[LE,RO]{\thepage}
%\fancyhead[CE]{\textit{JI QI, XIN TANG AND XICAN XI}}
%\fancyhead[CO]{\textit{THE SIZE DISTRIBUTION OF FIRMS AND INDUSTRIAL POLLUTION}}
\cfoot{}
\renewcommand{\headrulewidth}{0pt}
%\renewcommand*\footnoterule{}
%\setcounter{page}{1}

@@

\title{\vspace{-1cm}\Large{\textsf{The Size Distribution of Firms and Industrial Water Pollution: A Quantitative Analysis of China} \\ \textsf{Replication Instruction}}}
\author{
  \normalsize{{Ji Qi}} \\
  \normalsize{{Chinese Academy of Environmental Science}}
  \and
  \normalsize{{Xin Tang}}\footnote{Corresponding Author: zjutangxin@gmail.com} \\
  \normalsize{{Wuhan University}} \\
  \normalsize{{International Monetary Fund}}
  \and
  \normalsize{{Xican Xi}} \\
  \normalsize{{Fudan University}}
}
\date{\normalsize\today}

>>>>

% Set header and footer
\usepackage{fancyhdr}
\pagestyle{fancy}
\fancyhead{}
\fancyhead[LE,RO]{\thepage}
\fancyhead[CE]{\textit{AMERICAN ECONOMIC JOURNAL: MACROECONOMICS}}
\fancyhead[CO]{\textit{QI ET AL.: FIRM SIZE DISTRIBUTION AND POLLUTION REPLICATION}}
\cfoot{}
\renewcommand{\headrulewidth}{0pt}
%\renewcommand*\footnoterule{}
%\setcounter{page}{1}

@@

\title{\vspace{-1cm}\Large{\textsf{The Size Distribution of Firms and Industrial Water Pollution: A Quantitative Analysis of China} \\ \textsf{Replication Instructions}}}
\author{
  \normalsize{{Ji Qi}} \\
  \normalsize{{Chinese Academy of Environmental Science}}
  \and
  \normalsize{{Xin Tang}}\footnote{Corresponding Author: zjutangxin@gmail.com} \\
  \normalsize{{Wuhan University}} \\
  \normalsize{{International Monetary Fund}}
  \and
  \normalsize{{Xican Xi}} \\
  \normalsize{{Fudan University}}
}
\date{\normalsize\today}
